---
title: "Base R Statistics"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

[Home](index.html)

```{r eval=T, echo=F, message=F}
library(tidyverse)
library(dslabs)
```


### Generating sequences 
Normal sequence
```{r eval=T, echo=T}
x <- seq(1:10)
x
```
Odd numbers only
```{r eval=T, echo=T}
x.odd <- seq(1,10,2)
x.odd
```
Even distribution between ranges. Example: 3 equal division between 1 and 10.
```{r eval=T, echo=T}
y.divide <- seq(1,10, length.out = 3)
y.divide
```

***

### Monte Carlo Simulations 
#### Discrete
Monte Carlo simulations model the probability of different outcomes by repeating a random process a large enough number of times that the results are similar to what would be observed if the process were repeated forever.
First, create an box with data. This can be done through **rep** (2 red, 3 blue balls:
```{r eval=T, echo=T}
beads <- rep(c("red", "blue"), times = c(2,3))
beads
```
Lets pick a bead from this box 10,000 times. To do this, we set up *B* and run it.
```{r eval=T, echo=T}
B <- 100000    
events <- replicate(B, sample(beads, 1))    # draw 1 bead, B times
tab <- table(events)    # make a table of outcome counts
prop.table(tab)    # view table of outcome proportio
```
#### Continuous
Generating simulated height data using normal distribution.
```{r eval=T, echo=T}
x <- heights %>% filter(sex=="Male") %>% pull(height)
n <- length(x)
avg <- mean(x)
s <- sd(x)
simulated_heights <- rnorm(n, avg, s)
```
The **sumulated_heights** is built from the length, mena, and sd. The plot of this is as follows. Important to note that this is built from the assumption of normal distribution:
```{r eval=T, echo=T}
data.frame(simulated_heights = simulated_heights) %>%
    ggplot(aes(simulated_heights)) +
    geom_histogram(color="black", binwidth = 2)
```
Example, running a monte carlo simulation to find out the probablity of people over 7 feet (answer: *0.0214*). Running the simulation 10,000 times (B):
```{r eval=T, echo=T}
set.seed(3233)
B <- 10000
tallest <- replicate(B, {
    simulated_data <- rnorm(800, avg, s)    # generate 800 normally distributed random heights
    max(simulated_data)    # determine the tallest height
})
mean(tallest >= 7*12) #7*12 = 84 inches, which is 7 feet. 
```
Important to note the **set.seed()** function allows us to control the random. Without this function, the answer would be different because you cannot control the random variability. But with set.seed() you will have the same answer every time.

***

### Mean / Sd
For mean, median, sd, min, max:
```{r eval=F, echo=T}
heights %>%
    filter(sex == "Male") %>%
    summarize(average=mean(height), sd=sd(height), median = median(height),
              minimum = min(height), maximum = max(height))
```
***
### Observing Columns 
**murders** is the dataset. To observe the column types,
```{r eval=T, echo=T}
str(murders)
```
To observe all column numbers. Easy to see which column is which number.
```{r eval=T, echo=T}
names(murders)
```
To observe the first 5 data data of a column.
```{r eval=T, echo=T}
murders$state[1:5]
```
***
### Data Frames (Vectors) 
Associating vectors only
```{r eval=T, echo=T}
city <- c("Tokyo", "Lile", "Dover")
area <- c(10, 8, 13)
names(area) <- city
area
```
Creating Data Frames. Extra column created because of previous code.
```{r eval=T, echo=T}
data <- data.frame(name=city, value=area)
data
```
***
### Normal Distribution 
#### q-q graph ####
```{r eval=T, echo=F}
data("heights")
male <- heights %>% 
  filter(sex=="Male")
```
To see if **male** dataset follow a normal distribution. First define **p** as quantile ranges from 0.05 to 0.95.
```{r eval=T, echo=T}
p <- seq(0.05, 0.95, 0.05)
```
The **observed_q** is the real quantile of your dataset. The **theory_q** is the expected quantiles of a normal distribution. 
```{r eval=T, echo=T}
observed_q <- quantile(male$height, p)
theory_q <- qnorm(p, mean=mean(male$height), sd=sd(male$height))
```
The see closely they match, simply plot them. This shows that points almost match, so male dataset is a good approximation for normal distribution.
```{r eval=T, echo=F}
plot(theory_q, observed_q)
abline(0,1)
```
***




***