---
title: "Base R Analysis"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

[Home](index.html)

```{r eval=T, echo=F, message=F}
library(tidyverse)
library(dslabs)
```
***
### Observing Columns ###
**murders** is the dataset. To observe the column types,
```{r eval=T, echo=T}
str(murders)
```
To observe all column numbers. Easy to see which column is which number.
```{r eval=T, echo=T}
names(murders)
```
To observe the first 5 data data of a column.
```{r eval=T, echo=T}
murders$state[1:5]
```
***

***
### Generating sequences ###
Normal sequence
```{r eval=T, echo=T}
x <- seq(1:10)
x
```
Odd numbers only
```{r eval=T, echo=T}
x.odd <- seq(1,10,2)
x.odd
```
Even distribution between ranges. Example: 3 equal division between 1 and 10.
```{r eval=T, echo=T}
y.divide <- seq(1,10, length.out = 3)
y.divide
```
***
### Data Frames (Vectors) ###
Associating vectors only
```{r eval=T, echo=T}
city <- c("Tokyo", "Lile", "Dover")
area <- c(10, 8, 13)
names(area) <- city
area
```
Creating Data Frames. Extra column created because of previous code.
```{r eval=T, echo=T}
data <- data.frame(name=city, value=area)
data
```

***

