---
title: "Data Visualization"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

[Home](index.html)

***

```{r eval=T, echo=F, warning=F, message=F}
library(readxl)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(ggrepel)
library(ggthemes)
library(dslabs)
LAC <- read_excel("data/honors_lac.xlsx", 
                  sheet = "Latin America & Caribbean")
```

### Histogram
```{r eval=T, echo=F}
hist <- heights %>% 
  filter(sex=="Male")
```
Histogram. Change binwidth to alter the shape of the slopes.
```{r eval=T, echo=F}
ggplot(hist, aes(x=height))+
  geom_histogram(binwidth = 1, fill = "blue", col = "black") +
    xlab("Male heights in inches") +
    ggtitle("Histogram")
```
To create a smooth histogram (more similar to normal distribution graphs)
```{r eval=T, echo=T}
ggplot(hist, aes(x=height))+
  geom_density(fill = "green2")
```
#### Histogram (different bin levels)
gg.arrange used to see how different binwidth affects different histograms. Needs package **gridExtra**.
```{r eval=T, echo=T}
p <- heights %>% filter(sex == "Male") %>% ggplot(aes(x = height))
p1 <- p + geom_histogram(binwidth = 1, fill = "blue", col = "black")
p2 <- p + geom_histogram(binwidth = 2, fill = "blue", col = "black")
p3 <- p + geom_histogram(binwidth = 3, fill = "blue", col = "black")

grid.arrange(p1, p2, p3, ncol = 3)
```

***
### Q-Q Plot
Basic qq plot:
```{r eval=T, echo=T}
p1 <- heights %>% filter(sex == "Male") 
ggplot(p1, aes(sample = height))+
  geom_qq()
```

***
### Line Plot 
```{r eval=T, echo=T}
ggplot(LAC, aes(x=Year))+
  geom_line(aes(y=Yield_r), color="Green3", size=1)+
  geom_line(aes(y=Area_r), color="Green3", linetype="dashed", size=1)+
  labs(title="Latin America & Caribbean", x="Year", y="Relative Change")+
  theme_bw(base_size = 12)+
  coord_cartesian(ylim=c(80, 140))+
  scale_y_continuous(breaks = seq(80, 140, 10))+
  scale_x_continuous(breaks = seq(2002, 2016, 2))+
  geom_segment(aes(x=2002, y=100, xend=2016, yend=100), size=0.5)
```

***

### Scatterplot 
#### Harvard Course Example 
First a code to calculate summary statistics to put on graph.
```{r eval=T, echo=T}
summary_r <- murders %>%
    summarize(rate = sum(total) / sum(population) * 10^6) %>%
    .$rate
```
The code for plot:
```{r eval=T, echo=T}
ggplot(murders, aes(x=population/10^6, y=total, label = abb)) +
    geom_abline(intercept = log10(summary_r), lty = 2, color = "darkgrey") +
    geom_point(aes(col = region), size = 3) +
    geom_text_repel() +
    scale_x_log10() +
    scale_y_log10() +
    labs(title = "US Gun Murders in 2010", x="Population in millions (log scale)",
         y="Total number of murders (log scale)")+
    scale_color_discrete(name = "Region") +
    theme_economist()
```

#### Country - Name 
```{r eval=T, echo=F, message=F, warning=F, error=F}
data0 <- read_csv("data/honors_baseline.csv")

data1 <- data0 %>% 
  select(2,3,5,6,13)
data2 <- data1 %>%
  filter(Year=="2016")
```

```{r eval=T, echo=T, message=F, warning=F, error=F}
ggplot(data2, aes(x=log(GDP_capita), y=log(Fertilizer_use), color=Region))+
  geom_point()+
  geom_text(aes(label=Country), hjust=1, vjust=0)+
  labs(title="Fertilizer Use (2016)", x="Log(GDP per Capita)", y="Log(Fertilizer Use)")+
  theme_classic(base_size = 12)+
  coord_cartesian(xlim=c(5.5, 11.2))
```

***


