---
title: "Regression"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

[Home](index.html)

***

### Panel Regression ###
Library: stargazer, knitr, sandwitch, lmtest, AER, forecast, plm. These contain more than necessary packages required for panel regression.
The first step is to make your data frame into a panel form.
```{r eval=F, echo=T}
panel <- pdata.frame(data, index=c("Country", "Year"))
```
For fixed effects model (two-way - country and year)
```{r eval=F, echo=T}
fixed.effect <- plm(y~x1+I(x1^2)+x2+x3, 
                 data=panel, model="within", effect = "twoway")
```
For random effects model
```{r eval=F, echo=T}
random.effect <- plm(y~x1+I(x1^2)+x2+x3, 
                 data=panel, model="random")
```
To view these models without and with standard error.
```{r eval=F, echo=T}
stargazer(random.effect, type='text')
stargazer(coeftest(random.effect, vcovHC), type="text")
```
Hausman test to verify if to use fixed effect or random effect. If p < 0.05, use fixed effects model.
```{r eval=F, echo=T}
phtest(fixed.effect, random.effect)
```
***







