---
title: "Regression"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

```{r eval=T, echo=F, message=F, warning=F}
library(tidyverse)
library(HistData) #Historical data is found from this package

data("GaltonFamilies")
galton_height <- GaltonFamilies
```

[Home](index.html)

### Correlation
One of the first things to do before performing a regression is correlation. Correlation is between **-1** to **1**.
```{r eval=T, echo=T}
r <- galton_height %>% 
  summarize(r = cor(father, childHeight))
r
```

### Panel Regression 
Library: stargazer, knitr, sandwitch, lmtest, AER, forecast, plm. These contain more than necessary packages required for panel regression.
The first step is to make your data frame into a panel form.
```{r eval=F, echo=T}
panel <- pdata.frame(data, index=c("Country", "Year"))
```
For fixed effects model (two-way - country and year)
```{r eval=F, echo=T}
fixed.effect <- plm(y~x1+I(x1^2)+x2+x3, 
                 data=panel, model="within", effect = "twoway")
```
For random effects model
```{r eval=F, echo=T}
random.effect <- plm(y~x1+I(x1^2)+x2+x3, 
                 data=panel, model="random")
```
To view these models without and with standard error.
```{r eval=F, echo=T}
stargazer(random.effect, type='text')
stargazer(coeftest(random.effect, vcovHC), type="text")
```
Hausman test to verify if to use fixed effect or random effect. If p < 0.05, use fixed effects model.
```{r eval=F, echo=T}
phtest(fixed.effect, random.effect)
```

***

### ARIMA Forecast 
First convert the dataset into time-series form. We can see this through the plot().
```{r eval=F, echo=T}
temp.ts <- ts(temp, start=1998, end=2017, frequency = 1)
plot(temp.ts)
```
The basic steps for the ARIMA prediction are as follows. Do not know the detail, but this looks at historical data to predict future trends. It is one variable dependent, meaning interactions are harder to integrate. 

```{r eval=F, echo=T}
arima.temp <- arima(temp.ts, order=c(3,1,1))
summary(arima.temp)
plot(forecast(arima.temp, 5))
forecast(arima.temp, 5)
```

***




